Blocking-resistant communication\\through domain fronting

### 2014-07-25 docs/meek.tex
More generic caption for architecture diagram.

\begin{figure*}
\centering
\includegraphics[width=\linewidth]{architecture}
\caption{
Architecture of meek.
The Google frontend server is the server that dispatches requests to different services depending on the Host header.
Components that are new in our system are outlined in blue.
The ``Google infrastructure'' block may be replaced by other infrastructure that supports domain fronting.
}
\label{fig:architecture}
\end{figure*}

>>>>

\begin{figure*}
\centering
\includegraphics[width=\linewidth]{architecture}
\caption{
Architecture of meek.
The client sends an HTTP request to the Tor bridge by way of an intermediate web service such as a CDN.
The client protects the bridge's domain name \textbf{forbidden.example} from the censor
by fronting it with another name, here \textbf{allowed.example}.
The intermediate web server decrypts the TLS layer and forwards the request to the bridge
according to the Host header.
The bridge sends data back to the client in the HTTP response.
\meekclient\ and \meekserver\ are transport plugins, the interface between Tor and meek.
The host actually at allowed.example does not participate in the communication.
}
\label{fig:architecture}
\end{figure*}
